---
title: "7_13"
author: "Rachel Slimovitch"
date: "2023-07-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, tidy.opts=list(width.cutoff=60),tidy=TRUE)
library(knitr)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(tableone)
set.seed(123)
```


Open data:
```{r}
merged_data<- read.csv("/Users/rachelslimovitch/Documents/22-23/Brown/Thesis and APE/Code_6_26/7_13_COVID_df2.csv")

merged_data <- merged_data %>%
  rename(Surveillance=surveillance) 
  
```

**Note:**
- covid_data is our output and is dim 1080x71 (3 runs for each unique parameter combination)
- each row represents a single iteration of the simulation
- column "class" is # classroom transmission cases
- had to decrease # options for mitigation in order to get it to run

Basic figures:
- mitigation on x-axis
- class transmission on y-axis
- stratified by either test type or surveillance

```{r}
ggplot(merged_data, aes(x=mitigation, y=class, color=test_days)) +
  geom_point() +
  xlab("Mitigation") + 
  ylab("Class")

ggplot(merged_data, aes(x = mitigation, y = class, color = test_type)) +
  stat_summary(fun = "mean", geom = "point") +
  xlab("Mitigation") +
  ylab("Average Class") +
  labs(fill = "Test Type")

```

Create a new df: average value of class for each unique combo of mitigation level, test_type, surveillance
```{r}
df_surveil_facet <- merged_data %>%
  mutate(mitigation_group = ifelse(mitigation %in% c(0.2, 0.35), "Low", 
                           ifelse(mitigation == 0.5, "Middle", "High"))) %>%
  mutate(mitigation_group = factor(mitigation_group, levels = c("Low", "Middle", "High"))) %>%
  group_by(mitigation_group, Surveillance, test_type) %>%
  summarize(average_class = mean(class)) %>%
  ungroup()

df_day_facet<- merged_data %>%
  mutate(mitigation_group = ifelse(mitigation %in% c(0.2, 0.35), "Low", 
                           ifelse(mitigation == 0.5, "Middle", "High"))) %>%
  mutate(mitigation_group = factor(mitigation_group, levels = c("Low", "Middle", "High"))) %>%
  group_by(mitigation_group, test_days, test_type) %>%
  summarize(average_class = mean(class)) %>%
  ungroup()
```

Now, plot this:

```{r}

ggplot(df_surveil_facet, aes(x = mitigation_group, y = average_class, group = test_type, color = test_type)) +
  geom_line() +
  facet_wrap(~ Surveillance) +
  xlab("Mitigation") +
  ylab("Average Class")

ggplot(df_day_facet, aes(x = mitigation_group, y = average_class, group = test_type, color = test_type)) +
  geom_line() +
  facet_wrap(~ test_days) +
  xlab("Mitigation") +
  ylab("Average Class")


```
What about if we just show staff vs. all?
```{r}
df_surveil_facet_nostudents <- df_surveil_facet %>%
  filter(test_type!="students")
```

```{r}
library(ggrepel)

# Add numbers to each plot
df_numbers <- df_surveil_facet_nostudents %>%
  group_by(Surveillance, test_type, mitigation_group) %>%
  summarize(x = max(as.integer(mitigation_group)), y = max(average_class))

ggplot(df_surveil_facet_nostudents, aes(x = mitigation_group, y = average_class, group = test_type, color = test_type, linetype = test_type)) +
  geom_line(size = 1) +
 #add text
 geom_text_repel(
    data = df_numbers,
    aes(x = x, y = y, label = round(y, 2)),
    size = 3,
    nudge_x = -0.1,  # Adjust horizontal positioning of labels
    segment.size =5,  # Increase the size of segments for repelling labels
    direction = "y",  # Only repel labels vertically
    segment.color = NA,  # Remove segment lines
  ) +
  #faceting and labels
  facet_wrap(~ Surveillance, nrow = 1, strip.position = "top") +
    labs(
    title="Average classroom transmission by mitigation level, \nstratified by population tested and surveillance efforts",
    x="Mitigation",
    y="Average classroom transmission over 30 days"
  ) +
  #add themes and colors
  scale_color_manual(values = c("black", "gray30")) +
  scale_linetype_manual(values = c("dotted","solid")) +  # Different line types
  ylim(0,9) +
  theme_bw() +
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
       strip.background = element_blank(),
        strip.text = element_text(size = 12),
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        axis.title = element_text(colour = "black"),
        plot.margin = margin(1, 1, 1, 1, "cm"),
        plot.title = element_text(hjust = 0.5)) +
  guides(
    linetype = guide_legend(
      override.aes = list(
        color = "black",  # Set line color to black
        shape = NA  # Remove shape legend
      )))



```



With no facet: **This is currently Figure 1 on the abstract.**

```{r}
df_mitigation_testtype <- merged_data %>%
  mutate(mitigation_group = ifelse(mitigation %in% c(0.2, 0.35), "Low", 
                           ifelse(mitigation == 0.5, "Middle", "High"))) %>%
  mutate(mitigation_group = factor(mitigation_group, levels = c("Low", "Middle", "High"))) %>%
  group_by(mitigation_group, test_type) %>%
  summarize(average_class = mean(class)) %>%
  ungroup()
```



```{r}
# Add numbers to each plot
df_numbers <- df_mitigation_testtype %>%
  group_by(test_type, mitigation_group) %>%
  summarize(x = max(as.integer(mitigation_group)), y = max(average_class))

ggplot(df_mitigation_testtype, aes(x = mitigation_group, y = average_class, group = test_type, color = test_type, linetype = test_type)) +
  geom_line(size = 1) +
 #add text
 geom_text_repel(
    data = df_numbers,
    aes(x = x, y = y, label = round(y, 2)),
    size = 3,
    nudge_x = -0.1,  # Adjust horizontal positioning of labels
    segment.size =5,  # Increase the size of segments for repelling labels
    direction = "y",  # Only repel labels vertically
    segment.color = NA,  # Remove segment lines
  ) +
  #labels
    labs(
    title="Average classroom transmission by mitigation level, \nstratified by population tested",
    x="Mitigation",
    y="Average classroom transmission over 30 days"
  ) +
  #add themes and colors
  scale_color_manual(values = c("black", "gray30", "gray20")) +
  scale_linetype_manual(values = c("dotted","solid", "dashed")) +  # Different line types
  ylim(0,9) +
  theme_bw() +
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
       strip.background = element_blank(),
        strip.text = element_text(size = 12),
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        axis.title = element_text(colour = "black"),
        plot.margin = margin(1, 1, 1, 1, "cm"),
        plot.title = element_text(hjust = 0.5)) +
  guides(
    linetype = guide_legend(
      override.aes = list(
        color = "black",  # Set line color to black
        shape = NA  # Remove shape legend
      )))

```

Without averaging class: get stuck.

```{r}

df_surveil_facet <- merged_data %>%
  mutate(mitigation_group = ifelse(mitigation %in% c(0.2, 0.35), "Low", 
                                   ifelse(mitigation == 0.5, "Middle", "High"))) %>%
  mutate(mitigation_group = factor(mitigation_group, levels = c("Low", "Middle", "High")))

ggplot(df_surveil_facet, aes(x = mitigation_group, y = class, color = test_type)) +
  geom_point() +
  facet_wrap(~ surveillance) +
  xlab("Mitigation") +
  ylab("Class")

```
