---
title: "7_3"
author: "Rachel Slimovitch"
date: "2023-07-03"
output: pdf_document
---

*##############################################################################*
**COVID WILD TYPE:**
- no vaccination
- see 7_3 Try 1 for COVID-19 code w/vaccination (delta variant)

*##############################################################################*

Set up libraries:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, tidy.opts=list(width.cutoff=60),tidy=TRUE)
library(tidyverse)
library(BackToSchool)
library(tictoc)
library(igraph)
library(foreach)
library(doMC)
library(dplyr)
library(data.table)
library(parallel)
library(here)
```

Run the ABM: abm_correction.R

Then continue:
-  load a synthetic population
```{r}
data(synthMaryland)
options(warn = 2)
```

####************************** FUNCTIONS TO VARY PARAM SETS **************************####   
  
**Run single iteration:**      
- *sims fcn*: uses input parameters to call mult_runs function (run model multiple times)

```{r}
sims = function(df, synthpop, class = NA, job.no = "0"){
  #set.seed(i)
  i = 1 #in this case, running 1 time
  out = mult_runs(version = df$version[i], 
                  N = 1, 
                  n_contacts = df$n_contacts[i], 
                  n_staff_contact = df$n_staff_contact[i],
                  run_specials_now = df$run_specials_now[i], 
                  start_mult = df$start_mult[i], 
                  high_school = df$high_school[i],
                  attack = df$attack.df[i], 
                  child_susp = df$child_susp[i], 
                  time = df$time[i], 
                  synthpop = synthpop,
                  rel_trans = df$rel_trans[i], 
                  n_other_adults = df$n_other_adults[i], 
                  n_class = df$n_class[i],
                  notify = df$notify[i], 
                  test = df$test[i], 
                  dedens = df$dedens[i], 
                  num_adults = df$num_adults[i], 
                  teacher_trans = df$teacher_trans[i],
                  start_type = df$start_type[i], 
                  child_trans = df$child_trans[i], 
                  type = df$type[i],
                  days_inf = df$days_inf[i], 
                  disperse_transmission = df$disperse_transmission[i], 
                  n_start = df$n_start[i],
                  total_days = df$total_days[i],
                  teacher_susp = df$teacher_susp[i], 
                  mult_asymp = df$mult_asymp[i], 
                  mult_asymp_child = df$mult_asymp_child[i],
                  isolate = df$isolate[i], 
                  test_sens = df$test_sens[i], 
                  test_frac = df$test_frac[i],
                  p_asymp_adult = df$p_asymp_adult[i], 
                  p_asymp_child = df$p_asymp_child[i],
                  p_subclin_adult = df$p_subclin_adult[i], 
                  p_subclin_child = df$p_subclin_child[i],
                  child_prob = df$child_prob[i], 
                  adult_prob = df$adult_prob[i], 
                  class = class,
                  test_days = df$test_days[i], 
                  test_type = df$test_type[i], 
                  no_test_vacc = df$no_test_vacc[i], 
                  rel_trans_HH = df$rel_trans_HH[i], 
                  rel_trans_HH_symp_child = df$rel_trans_child_symp_HH[i],
                  rel_trans_CC = df$rel_trans_CC[i], 
                  n_HH = df$n_HH[i],
                  quarantine.length = df$quarantine.length[i], 
                  quarantine.grace = df$quarantine.grace[i], 
                  turnaround.time = df$turnaround.time[i],
                  test_start_day = df$test_start_day[i], 
                  family_susp = df$family_susp[i], 
                  test_quarantine = df$test_quarantine[i], 
                  vax_eff = df$vax_eff[i], 
                  child_vax = df$child.vax[i], 
                  time_seed_inf = df$time_seed_inf[i], 
                  seed_asymp = df$seed_asymp[i], 
                  surveillance = df$surveillance[i], 
                  overdisp_off = df$overdisp_off[i], 
                  include_weekends = df$include_weekends[i], 
                  rel_trans_adult = df$rel_trans_adult[i], 
                  rapid_test_sens = df$rapid_test_sens[i],
                  adult_unvax_hosp_rate = df$adult_unvax_hosp_rate[i], 
                  child_unvax_hosp_rate = df$child_unvax_hosp_rate[i], 
                  adult_vax_hosp_rate = df$adult_vax_hosp_rate[i], 
                  child_vax_hosp_rate = df$child_vax_hosp_rate[i])
  
  out <- bind_cols(out, df[i,!(colnames(df) %in% c("surveillance"))])
  
  #save(out, file = paste0("results", i, ".RData"))
  #rm(out)
  return(out)
}

```


**Run in parallel:**  
- enable code to run multiple tasks simultanenously by using multiple CPU cores
```{r}
doMC::registerDoMC(cores = detectCores())
detectCores()
foreach::getDoParWorkers()

```

Takes input parameters:  
- iterates over each row of df; calling sims function for each row and combining results w/rbind
**QUESTION:**AM I CORRECT IN CHANGING THIS TO PASS IN df[i,] INSTEAD OF df[1,]
```{r}
run_parallel = function(df, synthpop, class = NA){  
  
  # repeat each row ntot times
  df <- df[rep(row.names(df), df$n_tot),] %>% mutate(i = row_number())
  
  # run each row
  foreach(i=1:nrow(df), .combine = "rbind") %dopar% {sims(df[i,], synthpop, class = class)}
}

```


####************************** DEFINE SIMULATION SCENARIOS **************************####

Set hospitalization parameters:
```{r}
adult.ifr <- 500/1e6 #adult infection fatality rate
child.ifr <- 20/1e6  #child infection fatality rate

adult.p.die_hosp <- 2.1e-2 #adult prob of dying in hospital
child.p.die_hosp <- 0.7e-2 #child prob of dying in hospital

adult.p_hosp <- round(adult.ifr/adult.p.die_hosp,3) #infection fatality rate
child.p_hosp <- round((24/63.7)*child.ifr/child.p.die_hosp,3) #Conversion factor is for 5-11 vs <17

```

**Set up base simulations:**
- create df called df_ELEM.temp, where mitigation varies from 0 to 0.9999, prob stays 30/100,000; and other variables remain constant

```{r}
df_ELEM.temp <- expand_grid(mitigation = c(seq(from = 0, to = 0.99, by = 0.05), 0.9999),
                            prob = 30/100000) %>%
  mutate(start_type = "cont", 
         n_HH = 1, test_days = "week",
         test_type = "all", 
         test_sens = .8,
         total_days = 5, 
         run_specials_now = T,
         child_trans = 0.5, 
         teacher_trans = 1, 
         high_school = F,
         p_asymp_adult = .2, 
         p_asymp_child = 0.4,
         p_subclin_adult = .2, 
         p_subclin_child = 0.4,
         mult_asymp = .5, 
         mult_asymp_child = 1, 
         quarantine.length = 5, 
         quarantine.grace = 3,
         turnaround.time = 0, 
         n_other_adults = 30, 
         n_class = 5,
         test_quarantine = T,  
         disperse_transmission = F, 
         dedens = 1 , n_start = 0, 
         days_inf = 5, time = 30, 
         n_contacts = 10,
         n_staff_contact = 5, 
         rel_trans_child_symp_HH = 1/child_trans, 
         rel_trans = 1/8, 
         start_mult = 0, #disperse = T, DONT THINK I NEED DISPERSE??
         test_start_day = 1, 
         n_tot = 1, 
         isolate = T, 
         no_test_vacc = F, 
         time_seed_inf = NA, 
         seed_asymp = F, 
         surveillance = F, 
         overdisp_off = T, 
         num_adults = 2, 
         version = 2, 
         include_weekends = T, 
         rel_trans_adult = 2,  
         rapid_test_sens = 0.8,
         adult_unvax_hosp_rate = adult.p_hosp, 
         child_unvax_hosp_rate = child.p_hosp, 
         adult_vax_hosp_rate = 0, 
         child_vax_hosp_rate = 0) 

```


Set up simulation for delta variant:
```{r}
df_ELEM.delta =  df_ELEM.temp %>% #take df_ELEM temp and:
  expand_grid(type = c("base"), #don't need b/c default, but could add
              variant.attack = c(0.07), #need if I keep rel_trans_HH and rel_trans_CC
              vax.rates = c("t50.c0", "t50.c25", "t50.c50", "t70.c0", "t70.c25", "t70.c50", "t70.c70"), #don't need (set=0)
              notify.scenario = c("yes.wo.test", "yes.w.test90"), #only need this to vary notify between false and true
              vax_eff = c(0.7)) %>% #need this if we keep child_prob and adult_prob the way they currently are
  
  mutate(attack.df = variant.attack*(1-mitigation), #modifies grid above
         child.vax = ifelse(vax.rates == "t50.c0" | vax.rates == "t70.c0", 0,
                            ifelse(vax.rates == "t50.c25" | vax.rates == "t70.c25", 0.25,
                                   ifelse(vax.rates == "t50.c50" | vax.rates == "t70.c50", 0.5,
                                          ifelse(vax.rates == "t70.c70", 0.7, -1)))),
         teacher_susp = ifelse(vax.rates == "t50.c0" | vax.rates == "t50.c25" | vax.rates == "t50.c50", 0.5, 0.7),
         child_susp = 0.5,
         family_susp = teacher_susp,
         notify = ifelse(notify.scenario == "no", FALSE, TRUE),
         test = ifelse(notify.scenario == "yes.w.test90" | notify.scenario == "yes.w.test100", TRUE, FALSE),
         test_frac = ifelse(notify.scenario == "yes.w.test90", 0.9, ifelse(notify.scenario == "yes.w.test100", 1, 0)))

```


Then, assign df_ELEM to df_ELEM.delta:

```{r}
df_ELEM<-df_ELEM.delta
#df_ELEM <- rbind(df_ELEM.delta, df_ELEM.delta.vax.eff, df_ELEM.high_vax_coverage, df_ELEM.prev.variants)

```

Set the number of runs that we want to run per scenario:
```{r}
nsamp <- 100 #run 100 trials per scenario

```

Edit the dataframe to include row # (i), as well as:  
- n_tot is assigned value of nsamp (100)
- rel_trans_HH and rel_trans_CC are calculated
```{r}
df_ELEM <- df_ELEM %>% mutate(i = row_number(), n_tot = nsamp, rel_trans_HH = 2*variant.attack/attack.df, rel_trans_CC = variant.attack/attack.df)

```


Make class:  
- call the make_school function, using synthpop and n_class (# classes/grade) and n_other_adults (# adults in school other than primary teachers)
```{r}
class = make_school(synthpop = synthpop, n_other_adults = df_ELEM$n_other_adults[1], 
                    includeFamily = T, n_class = df_ELEM$n_class[1])

```


####************************** RUN CODE **************************####
Assign df to the second row (just for now, to see output)

```{r}

#EDIT: IF I MAKE df_ELEM[1:3,] from df_ELEM[2,]
df<- df_ELEM %>% 
     mutate(prob = 39/100000, adult_prob = prob/((1-family_susp)+family_susp*(1-vax_eff)), 
                       child_prob = prob/((1 - child.vax)+child.vax*(1-vax_eff)), 
                       rel_trans_HH = 2*variant.attack/attack.df) #, n_tot=3) #changed from n_tot=1 (should be 100 @ end)

#Call run_parallel
#EDIT: IF I MAKE df_ELEM[1:3,] from df_ELEM[2,]
g = run_parallel(df_ELEM[1:5,] %>% 
                   mutate(prob = 39/100000, adult_prob = prob/((1-family_susp)+family_susp*(1-vax_eff)), 
                                        child_prob = prob/((1 - child.vax)+child.vax*(1-vax_eff)), 
                                        rel_trans_HH = 2*variant.attack/attack.df, n_tot = 3, sim_no = row_number()), #, n_tot=3),  #changed n_tot from 1
                 synthpop, class = class)
table(g$sim_no)
```

Save dataframe:
```{r}
write.csv(g, file="/Users/rachelslimovitch/Documents/22-23/Brown/Thesis and APE/Code_6_26/7_13_COVID_df.csv", row.names=FALSE)
```

See output:

```{r}
mean(g$tot)
mean(g$class)
threshold = 10
```
# We want largest g$prob (input) s.t. g$class (output) < some threshold
#NOTE: Results are output as an RData file for multiple sets of simulations simulation -- results must be bound into a single dataframe before generating the figures.

